### 2015-03-20 paper/paper.tex
asdf

We make each analysis a variable. For instance, the fifth line denotes
a hypothesis that the correct analysis of the 3rd item in the sentence
is \texttt{<V,Sg>}. We call this \texttt{Var 5}.

\begin{lstlisting}
((1,["the",<det>]),Lit v0)
((2,["bear",<n>,<sg>]),Lit v1)
((2,["bear",<vblex>,<pl>]),Lit v2)
((2,["bear",<vblex>,<fin>]),Lit v3)
((3,["sleep",<n>,<pl>]),Lit v4)
((3,["sleep",<vblex>,<sg>,<p3>]),Lit v5)
\end{lstlisting}

We have defined our variables, but not yet any truth values. We can
start by doing two things:
\begin{enumerate}
\item Make unambiguous tokens true by default: e.g. \texttt{Var 1}
  shows that the reading \texttt{Det} for the first token must be true.
\item Make hypotheses of possible n-grams. In the example below, we
show bigrams: \texttt{(Var 1 $\wedge$ Var 2) $\vee$ (Var 1 $\wedge$ Var 3)}
means that the first two tokens have analyses \texttt{Det,N} or
\texttt{Det,V}.
\end{enumerate}

We could easily add a third rule: for ambiguous tokens, make sure that
only one reading can be true (or a less strict version, where all
readings can't be true). For instance, \texttt{Not (Var 2 $\wedge$ Var
  3)} would be the constraint that the second token can't be both
\texttt{N} and \texttt{V} at the same time. However,
\cite{KarlssonTODO} argues that CG cannot remove genuine ambiguities;
in a case where a sentence is genuinely ambiguous, all readings are
returned.

\begin{lstlisting}
Var 1
Var 8
(Var 1 :&&: Var 2) :||: (Var 1 :&&: Var 3)
(Var 2 :&&: Var 4) :||: ((Var 2 :&&: Var 5) :||: ((Var 3 :&&: Var 4) :||: (Var 3 :&&: Var 5)))
(Var 4 :&&: Var 6) :||: ((Var 4 :&&: Var 7) :||: ((Var 5 :&&: Var 6) :||: (Var 5 :&&: Var 7)))
(Var 6 :&&: Var 8) :||: (Var 7 :&&: Var 8)
(Var 8 :&&: Var 9) :||: ((Var 8 :&&: Var 10))
\end{lstlisting}
% Not (Var 2 :&&: Var 3)
% Not (Var 4 :&&: Var 5)
% Not (Var 6 :&&: Var 7)
% Not (Var 9 :&&: Var 10)

@@

\subsection{Conflicts}
If you try to use conflicting rules, you get user error: mzero.

>>>>

We make each analysis a variable. For instance, the fifth line denotes
a hypothesis that the correct analysis of the 3rd item in the sentence
is \texttt{<V,Sg>}. We call this \texttt{v5}.

\begin{lstlisting}
((1,["the",<det>]),v0)
((2,["bear",<n>,<sg>]),v1)
((2,["bear",<vblex>,<pl>]),v2)
((2,["bear",<vblex>,<fin>]),v3)
((3,["sleep",<n>,<pl>]),v4)
((3,["sleep",<vblex>,<sg>,<p3>]),v5)
\end{lstlisting}

We have defined our variables, but not yet any truth values. We can
start by adding a clause that makes sure at least one variable in each
index is true:
\begin{enumerate}
\item \texttt{[v0]}
\item \texttt{[v1,v2,v3]}
\item \texttt{[v4,v5]}
\end{enumerate}

We could easily add a second rule: for ambiguous tokens, make sure that
only one reading can be true (or a less strict version, where all
readings can't be true). For instance, \texttt{Not (Var 2 $\wedge$ Var
  3)} would be the constraint that the second token can't be both
\texttt{N} and \texttt{V} at the same time. However,
\cite{KarlssonTODO} argues that CG cannot remove genuine ambiguities;
in a case where a sentence is genuinely ambiguous, all readings are
returned.

@@

\subsection{Ordering}

We had three strategies:
maximise: try to make as many rules true as possible;
maximise from top: apply rules from the beginning, discard rule if it
conflicts with the ones added;
discard from bottom: try to add all rules, if conflict, find which
conflict, and try again with only the rules that are in the list
before the first conflicting rule.

\subsection{Weird things}

mkVars: difference between options 1) and 2)

        mkVars :: [(Token,[Token])] -> (Bit -> Bit) -> [[Bit]]
1)        mkVars tctx f = [ f conseq:(map nt causes) | (t, ts) <- tctx
2)        mkVars tctx f = [ [nt cause,f conseq] | (t, ts) <- tctx
                                               , let conseq = getBit t
                                               , let causes = map getBit ts
                                               , cause <- causes ]

% Remove [[vblex]] (POS (AND (C (Exactly 0) (True,[[vblex,p1],[vblex,p2],[vblex,p3]])) (C (Barrier 1 [[cnjcoo],[cnjsub],[cnjadv],[rel]]) (True,[[vblex,p1],[vblex,p2],[vblex,p3]]))))
% [Lit ~v6,Lit ~v2]

We have rules:
REMOVE:r_como_1 Vblex (0 ("como") OR ("Como")) (*-1 Vblex BARRIER Cnj_Rel) ;
REMOVE:r_verb_1 Vblex (0 Vblex + Pers) (*1C Vblex + Pers BARRIER
Cnj_Rel) ;

And tokens:
((1,[">>>",>>>]),Lit v0)
((2,["<Jared>","*Jared"]),Lit v1)
((3,["<explica>","explicar",vblexfoo,pri,p3,sg]),Lit v2)
((3,["<explica>","explicar",vblex,imp,p2,sg]),Lit v3)
((4,["<como>","como",pr]),Lit v4)
((4,["<como>","como",rel,adv]),Lit v5)
((4,["<como>","comer",vblex,pri,p1,sg]),Lit v6)
((5,["<pequeñas>","pequeño",adj,f,pl]),Lit v7)
((6,["<diferencias>","diferencia",n,f,pl]),Lit v8)
((6,["<diferencias>","diferenciar",vblex,pri,p2,sg]),Lit v9)

In CG3, r_como_1 is applied first, and v6 is eliminated. r_verb_1
never has the Vblex+Pers condition available and is never triggered.
In CGSAT, neither is applied first; r_como_1 is is implication ``v2 =>
not v6'', ``v3 => not v6'' and r_verb_1 is ``v6 => not v2'' ``v6 => not v3''.

You can flip rules!

\begin{verbatim}
SELECT (det "<az>") IF (1 AdjOrN);
SELECT AdjOrN IF (-1 (det "<az>"));

REMOVE ("de" adv) IF (NOT 1C (adj));
REMOVE AllButAdj IF (-1 ("de" adv));
\end{verbatim}
